### 2016-02-14 pdocs/thesis/introduction.tex
more precise terms in introduction

Difference between elastic and plastic modulus is shown in \ref{fig:wp}. 
If stress is below yield limit, stress and strain are linear within cross section.
If cross section is fully plastic, stress is assumed to be at yield level over whole cross section and 
so plastic modulus is higher than elastic modulus.

Elastic part is often ignored in this work as displacements due to to elastic deformation are so small and 
related frequencies are so high.

@@

@@

>>>>

@@

Difference between elastic and plastic section modulus is shown in \ref{fig:wp}.

@@

If stress is below yield limit, stress and strain are linear within cross section.
If cross section is fully plastic, stress is assumed to be at yield level over whole cross section and 
so plastic section modulus is higher than elastic section modulus.

Elastic part is often ignored in this work as displacements due to to elastic deformation are small and 
related frequencies are high.
